Reproducibility and Open Science in Economics

### 2025-03-06 article.tex

>>>>

How onerous are access restrictions in general? In my work as Data Editor, it matters less than it would seem at first blush. The AEA asks that authors, when submitting, provide some information on how restrictive the data used in the article are, and whether the authors are able to provide the data editor with a not-for-publication copy, for the purpose of verification.\footnote{\href{https://www.aeaweb.org/journals/forms/data-code-availability}{Data and Code Availability Form}} Table~\ref{tab:categories} lists the four levels of restrictions, with some guidance on how to classify specific data. Authors can list multiple categories, and we review these, possibly adjusting them before we record them in our internal database.

\input{outputs/table_categories}

Table~\ref{tab:restrictions}
\input{outputs/table_access_provision}
